mouse_microbiome

### 2018-07-12 Manuscript_Mouse_Microbiome.Rmd
adding traits

# load packages and custom functions
wd <- 'C:\\Users\\John\\Documents\\msu\\Mouse_Microbiome\\'
setwd(wd)

@@

# load data
x_raw <- fread('C:\\Users\\John\\Google Drive\\Mouse_Microbiome_Shared_Files\\Data\\2018_06_12_run2_otus.csv')
tax <- fread('C:\\Users\\John\\Google Drive\\Mouse_Microbiome_Shared_Files\\Data\\otus_table_joined_taxa.txt')

@@

@@

>>>>

# load packages and custom functions
wd <- 'C:\\Users\\John\\Documents\\msu\\Mouse_Microbiome\\'
wd_dat <- 'C:\\Users\\John\\Google Drive\\Mouse_Microbiome_Shared_Files\\Data\\'
setwd(wd)

@@

# load data
x_raw <- fread(paste0(wd_dat, '2018_06_12_run2_otus.csv'))
tax <- fread(paste0(wd_dat, 'otus_table_joined_taxa.txt'))
traits <- readRDS(paste0(wd_dat, 'traits_castor_subtree_averaging.RDS')) %>%
  mutate(otu = as.integer(gsub('otu', '', otu)))

@@

#filter so trait table has only the same taxa.
#create wide version
traits <- filter(traits, otu %in% x$otu)
traits_wide <- spread(traits, trait, val, fill = NA)

@@

iwant <- c('Copies_16S','Forms_biofilms','Gene_number','Obligate_anaerobe','Sporulation')

tmp <- x %>%
  left_join(traits_wide[ ,c('otu', iwant)], by = 'otu') %>%
  gather(trait, val, .dots = iwant) %>%
  group_by(Mouse, Abx, Cohoused, Hour, trait) %>%
  filter(Cohoused != 'dead') %>%
  summarise(CWM = weighted.mean(val, w = abun)) %>%
  ungroup() %>%
  mutate(Abx = ifelse(Abx == 'Y', 'Abx', 'No abx'),
         Cohoused = ifelse(Cohoused == 'Y', 'Cohoused', 'Solitary'))

ggplot(tmp, aes(x = Hour, y = CWM, color = Abx)) +
    geom_rect(aes(xmin = 0, xmax = 120, ymin = -Inf, ymax = Inf), alpha = 0.3, fill = 'red', color = NA, data =  group_by(tmp, trait, Abx) %>% filter(row_number() == 1 & Abx == 'Abx')) +
    stat_smooth(aes(group = Abx), se = FALSE, size = 1.5) +
    stat_smooth(aes(lty = Cohoused, group = Mouse), geom="line", se = FALSE, alpha = 0.6) +
    scale_color_manual(values = c('red','black'), name = '') +
    scale_linetype_discrete(name = '') +
    facet_grid(trait~Abx, scales = 'free') +
    guides(lty=guide_legend(override.aes = list(color = 'black'))) +
    th
